---
title: "predictTTE Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{predictTTE Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

## Overview

`predictTTE` simulates future event trajectories from interim ADTTE records.
The package supports event-date predictions for target event counts and
event-count predictions for target dates.

## Inputs

Core columns expected in `data`:

- `usubjid`
- `trialsdt`
- `randdt`
- `adt`
- `cutoffdt`
- `status` (`1` event, `0` censored, `-1` dropout)
- `aval` (time from randomization to `adt` in days)

## Example

```{r eval=FALSE}
library(predictTTE)

adtte <- example_adtte_pfs

res <- predict_tte(
  data = adtte,
  planned_total_n = 176,
  target_events = c(120, 140, 160),
  target_dates = as.Date(c("2026-02-01", "2026-05-01", "2026-08-01")),
  nsim = 1000,
  assessment_intervals_days = c(42, 84),
  assessment_cut_days = c(365.25),
  enrollment_model = "exponential",
  event_model = "exponential",
  dropout_model = "exponential",
  ci_level = 0.95,
  fixed_parameters = TRUE,
  seed = 1
)

res$pred_dates
res$pred_event_counts
res$plot
res$pred_event_plot
```

## Notes

- Tumor assessment windows are handled by rolling latent event dates forward
  to the first post-event scheduled assessment.
- If `assessment_intervals_days = NULL` and `assessment_cut_days = NULL`,
  no tumor-assessment adjustment is applied.
- Current implementation supports `exponential`, `weibull`, `log-normal`,
  and `log-logistic` for model fitting/simulation.
